\LARGE \bf Mean Estimation from One-Bit Measurements

### 2020-12-01 proof-sgd.tex
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

These three definitions are linked in our case by a few important results.
First~\cite[Theorem 7.2]{VanDerVaart98}, if $\{P_\theta\}$ is QMD
(Def.~\ref{definition:qmd}) at the point $\theta$, then it is locally
asymptotically normal with $Z_n = \frac{1}{\sqrt{n}} \sum_{i = 1}^n
\score_\theta(X_i)$ and information matrix $I_\theta =
\E_\theta[\score_\theta \score_\theta^\top]$. Moreover, in any family
$\{P_\theta\}$ that is LAN (Def.~\ref{definition:lan}) at $\theta$, if $T_n$
is a regular estimator (Def.~\ref{definition:regular-estimator}) at $\theta$
with limiting distribution $Q$, then for any bounded, symmetric,
quasi-convex loss $L$ and $c < \infty$,
\begin{equation}
  \label{eqn:limit-law-regular}
  \limsup_n \sup_{\norm{h} \le c}
  \E_{P_{\theta + h/\sqrt{n}}}
  \left[L(\sqrt{n}(T_n - \theta - h / \sqrt{n}))\right]
  = \E[L(W)] ~~ \mbox{for~}W \sim Q
\end{equation}
(see Beran~\cite{beran1995role}, Eq.~(4.2)).
%
Thus, we show two results: first, that
that the family $\{P_\theta\}$ of distributions
defined by the shifted densities $\{f(\cdot - \theta)\}_{\theta \in \R}$
is quadratic-mean-differentiable at any $\theta$,
and second, that $\bar{\theta}_n$ is regular and
asymptotically normal.
The combination evidently gives the theorem.

@@

  We now verify that the setting of Theorem~\ref{thm:sgd}
  (and Lemma~\ref{lemma:sgd-median-regular}) satisfies the
  conditions of Corollary~\ref{corollary:polyak-juditsky}. First, we have
  the obvious fact that
  \begin{equation*}
    |\sgn(z) - \sgn(x + z)|
    \le 2 \cdot \indic{|x| \ge |z|}.
  \end{equation*}
  Recalling that the density $f$ is Lipschitz with median 0,
  for $\varphi(z) = \sgn(z)$, and $Z = X - \theta$ distributed with
  density $f$, we have
  \begin{align*}
    \ex{ \left| \varphi(Z) - \varphi(x + Z) \right| }
    \leq 2 \Prob\left( |Z_1| \le |x|  \right)
    = 2 \int_{-|x|}^{|x|} f(t) dt
    = 4 f(0)|x| \pm 2 \int_{-|x|}^{|x|}
    \lip(f) t dt
    = 4 f(0) |x| + 2 \lip(f) x^2
  \end{align*}
  where $\lip(f)$ is the Lipschitz constant of $f$.
  For large $x$ we always have
  $\E[|\varphi(Z) - \varphi(x + Z)|] \le 2$, so that
  condition~\eqref{eqn:additional-local-smooth} holds.
  In addition, we have
  \begin{equation*}
    \int_{\R} \varphi(x) f'(x ) dx
    = \int_{\R} \sgn(x) f'(x ) dx =
    \int_0^\infty f'(x ) dx
    - \int_{-\infty}^0 f'(x )
    = -2 f(0) = -\psi'(0).
  \end{equation*}
  Corollary~\ref{corollary:normal-expansion}
  now implies the convergence \eqref{eqn:sgd-median-regular}.
\end{proof}

>>>>

These three definitions are linked in our case by a few important results.
First~\cite[Theorem 7.2]{VanDerVaart98}, if $\{P_\theta\}$ is QMD
(Def.~\ref{definition:qmd}) at the point $\theta$, then it is locally
asymptotically normal with $Z_n = \frac{1}{\sqrt{n}} \sum_{i = 1}^n
\score_\theta(X_i)$ and information matrix $I_\theta =
\E_\theta[\score_\theta \score_\theta^\top]$. Moreover, in any family
$\{P_\theta\}$ that is LAN (Def.~\ref{definition:lan}) at $\theta$, if $T_n$
is a regular estimator (Def.~\ref{definition:regular-estimator}) at $\theta$
with limiting distribution $Q$, then for any bounded, symmetric,
quasi-convex loss $L$ and $c < \infty$,
\begin{equation}
  \label{eqn:limit-law-regular}
  \limsup_n \sup_{\norm{h} \le c}
  \E_{P_{\theta + h/\sqrt{n}}}
  \left[L(\sqrt{n}(T_n - \theta - h / \sqrt{n}))\right]
  = \E[L(W)] ~~ \mbox{for~}W \sim Q
\end{equation}
(see Beran~\cite{beran1995role}, Eq.~(4.2)).
%
Thus, we show two results: first,
that the family $\{P_\theta\}$ of distributions
defined by the shifted densities $\{f(\cdot - \theta)\}_{\theta \in \R}$
is quadratic-mean-differentiable at any $\theta$,
and second, that $\bar{\theta}_n$ is regular and
asymptotically normal.
The combination evidently gives the theorem.

@@

  We now verify that the setting of Theorem~\ref{thm:sgd}
  (and Lemma~\ref{lemma:sgd-median-regular}) satisfies the
  conditions of Corollary~\ref{corollary:polyak-juditsky}. First, we have
  the obvious fact that
  \begin{equation*}
    |\sgn(z) - \sgn(x + z)|
    \le 2 \cdot \indic{|x| \ge |z|}.
  \end{equation*}
  Recalling that the density $f$ is Lipschitz with median 0,
  for $\varphi(z) = \sgn(z)$, and $Z = X - \theta$ distributed with
  density $f$, we have
  \begin{align*}
    \ex{ \left| \varphi(Z) - \varphi(x + Z) \right| }
    \leq 2 \Prob\left( |Z_1| \le |x|  \right)
    = 2 \int_{-|x|}^{|x|} f(t) dt
    = 4 f(0)|x| + 2 \int_{-|x|}^{|x|}
    \lip(f) t dt
    = 4 f(0) |x| + 2 \lip(f) x^2
  \end{align*}
  where $\lip(f)$ is the Lipschitz constant of $f$.
  For large $x$ we always have
  $\E[|\varphi(Z) - \varphi(x + Z)|] \le 2$, so that
  condition~\eqref{eqn:additional-local-smooth} holds.
  In addition, we have
  \begin{equation*}
    \int_{\R} \varphi(x) f'(x ) dx
    = \int_{\R} \sgn(x) f'(x ) dx =
    \int_0^\infty f'(x ) dx
    - \int_{-\infty}^0 f'(x ) dx
    = -2 f(0) = -\psi'(0).
  \end{equation*}
  Corollary~\ref{corollary:normal-expansion}
  now implies the convergence \eqref{eqn:sgd-median-regular}.
\end{proof}
